Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-10-13 draft_lm1.tex
No more serotype differences; no more table of S0 ratios

% Results and Discussion can be combined.
\section*{Results}
% We only support three levels of headings, please do not create a heading level below \subsubsection.
%\subsection*{Subsection 1}
\subsection*{Serotype proportion}
The susceptible population estimated in this paper is defined as individuals 
susceptible to at least one of the circulating serotypes in any given year. 
Let this Total number of susceptibles be denoted by $S_T$.

Let the number of susceptibles to a given dengue virus ($DENV_i$), $S_i$ be 
represented by a Binomial random variables $S_i \sim Bin(n, p_i)$ where $n$ is 
population size and p is the true proportion of susceptibles to $DENV_i$ in 
the population, with $i \in  \{1, 2, 3, 4\}$. In the absence of 
cross-immunity, i.e., the exposure to serotypes are independent, the 
total number of susceptibles $S_T=\sum_i S_i$  should follow a Poisson-Binomial 
distribution, $PoisBin(p_i,n)$, where
\begin{equation}
 P(S_T=k) = \sum \prod_i p_i \prod_i  (1-p_i)
\end{equation}
\todo[inline]{this sum is over all types of susceptibles, I think: 
$\{S_{1}, S_{2}, 
S_{3},S_{4},S_{12},S_{123},S_{1234},S_{13},S_{14},S_{23},S_{234},S_{24},S_{34}\}
$}

Initially, we have no information about the distribution of the $p_i$ but they 
can be learned gradually with each epidemic.

Let $S_{0T}$ and $S_{fT}$, be the total number of susceptibles before and 
after an epidemic, respectively. The total number of cases observed in an 
epidemic, $I_T = \sum_i I_i$ can be expressed as $S_{0T}-S_{fT}$, thus
\begin{align}
 S_{fT} &= S_{0T} - I_T\\
 &=\sum S_{0i} - \sum I_i\\
 &=\sum_i S_{0i}-I_i
\end{align}

If $S_i/n \approx p_i$ and $I_i$ is observed, we can adjust the initial 
$p_i$ according to $I_i$.
\todo[inline]{sera que da para fazer inferencia bayesiana aqui?}

% the suceptibility can be manifested, in individuals, as one of 
% the following forms:
% \begin{equation}
%  S = \{S_{1}, S_{2}, S_{3}, 
% S_{4},S_{12},S_{123},S_{1234},S_{13},S_{14},S_{23},S_{234},S_{24},S_{34}\}
% \end{equation}

\section*{Discussion}
% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
LMC is grateful to Dr. Leonardo Bastos for useful discussions on the 
posterior inference for $R(t)$.

@@

\begin{table}
\caption{\bf{Table title}}
 \begin{center}
            \begin{tabular}{c|c}
            \hline
            Year & Ratio \\
            \hline
            1997 & 204.26(67.45-706.68)\\
1998 & 207.45 (170.45-261.63)\\
2000 & 2300.63 (1741.30-3156.85)\\
2001 & 317.62 (226.47-526.45)\\
2005 & 100.28 (48.95-171.58)\\
2006 & 198.26 (114.59-317.88)\\
2007 & 567.78 (388.55-834.58)\\
2008 & 7.82 (2.97-34.43)\\
1999 & 26.70 (5.97-87.36)\\

        \hline
        \end{tabular}
        \end{center}
\end{table}

>>>>

% Results and Discussion can be combined.
\section*{Results}
% We only support three levels of headings, please do not create a heading level below \subsubsection.
%\subsection*{Subsection 1}
\section*{Discussion}
% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
LMC is grateful to Dr. Leonardo Bastos for useful discussions on the 
posterior inference for $R(t)$.

@@
